Title

### 2012-12-05 inc/photocathode/plasmon/plasmon.tex
fix a couple nits

Collaborators at Argonne National Laboratory's Electron Microscopy Center, Material Science Division used a defocused Gallium focused ion beam (FIB) (Zeiss 1540XB) to iteratively mill an approximately sinusoidal shape into the surface of a silicon wafer.
Several regions were created each 100x100$\mu$m in area, having a $\sim$1$\mu$m period and $\sim$10\% modulation depth.
Given a laser wavelength of 523nm ($\varepsilon_{Au} \approx –3.95$ \cite{johnson_optical_1972}), this choice of periodicity corresponds by \ref{eq:plasmon_condition} to an incidence angle of $\sim39^{\circ}$, which is within the acceptance range of our experimental setup (35-75$^{\circ}$). %TODO point to Togawa section
An SEM image of one such region is shown in \ref{fig:fib-si-sem}.

@@

Using the Varian e-beam deposition chamber at the UIC Nano Core Facility (NCF), I deposited a thin layer of chromium as a binding agent, then a 300nm film of gold.
This thickness of gold is several times thicker than the skin depth of green light on gold, therefore the laser radiation cannot interact with the silicon.

>>>>

Collaborators at Argonne National Laboratory's Electron Microscopy Center, Material Science Division employed a defocused Gallium focused ion beam (FIB) (Zeiss 1540XB) to iteratively mill an approximately sinusoidal shape into the surface of a silicon wafer.
Several regions were created each 100x100$\mu$m in area, having a $\sim$1$\mu$m period and $\sim$10\% modulation depth.
Given a laser wavelength of 523nm ($\varepsilon_{Au} \approx –3.95$ \cite{johnson_optical_1972}), this choice of periodicity corresponds by \ref{eq:plasmon_condition} to an incidence angle of $\sim39^{\circ}$, which is within the acceptance range of our experimental setup (35-75$^{\circ}$). %TODO point to Togawa section
An SEM image of one such region is shown in \ref{fig:fib-si-sem}.

@@

Using the Varian e-beam deposition chamber at the UIC Nano Core Facility (NCF), I deposited a thin layer of chromium as a binding agent, then a 300nm film of gold.
This thickness of gold is several times thicker than the skin depth of green light on gold, therefore the laser radiation cannot interact with the silicon.
%TODO should I comment on the coating acting to smooth the surface to a proper sinusoid?
